Datasheets for Datasets: Enhancing Transparency and Accountability in Data Collection

### 2024-12-15 other/datasheet/datasheet_Hammer.qmd
Update the datasheet
fixed some error in datasheet

	-  The dataset does not include confidential information.

@@

	-  The data is factual and does not contain offensive content.

@@

	- No individuals can be identified from the dataset.

@@

	- No

@@

	- Data was collected through web scraping and API utilization from top grocers' websites.

@@

	- Data was obtained directly from publicly accessible websites.

@@

	- Not applicable, as data was collected from public sources.

@@

	- Regular audits ensured compliance with data protection standards.

@@

	- N/A

@@

	- No

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Data underwent cleaning to correct anomalies and impute missing values, ensuring high quality for analysis.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data is archived and available at https://jacobfilipp.com/hammer/
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	-  Preprocessing was performed using R scripts, with code available  at https://github.com/dawsonlll/Organic-Product-Pricing-Analysis.git
4. *Any other comments?*
	- No

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is publicly available for download.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	-  It is distributed in CSV and SQLite formats. No DOI found.
3. *When will the dataset be distributed?*
	- The dataset was made available on February 28, 2024
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is provided under MIT, encouraging academic and legal use.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- There are no known restrictions imposed by third parties.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply.
7. *Any other comments?*
	- No

>>>>

	-  No, the dataset does not contain any confidential or personally identifiable information. All data is publicly available and pertains to grocery prices listed on vendor websites.

@@

	- No, the dataset contains neutral information about grocery prices, which is unlikely to cause offense or anxiety.

@@

	- No, the dataset contains no personal identifiers or data that could be used to identify individuals.

@@

	- The dataset provides a valuable resource for analyzing pricing strategies and market trends in the grocery sector. It does not involve data from vulerable populations, does not contain any personally identifiable information, and no formal ethics review was conducted as the dataset does not involve sensitve or private data.

@@

	- The data was acquired through web scraping and API utilization from the websites of major grocery vendors. This data includes directly observable pricing and product details. Validation was performed by cross-referencing online prices with in-store checks and ensuring consistency across multiple data collection runs.

@@

	- The data was collected directly from publicly accessible grocery vendor websites.

@@

	- Not applicable, as the data was collected from publicly available online sources without involving individuals.

@@

	- Not applicable, as the dataset does not involve personal data or data from individuals. The focus is exclusively on publicly available product and pricing information.

@@

	- Not applicable, as no individual-level data requiring consent was collected.

@@

	- This dataset is a valuable tool for understanding pricing trends and consumer behaviour in the grocery market. However, users should note that this dataset focuses on publicly accessible data and has inherent limitations in representing small or independent retailers.

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, the data underwent preprocessing and cleaning to address anomalies and missing values. Steps included correcting outliers, imputing missing values, and ensuring consistency in product names and vendor labels. The cleaned data was prepared to support accurate and meaningful analysis
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data is archived and available at https://jacobfilipp.com/hammer/
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	-  Preprocessing was performed using R scripts, with code available  at https://github.com/dawsonlll/Organic-Product-Pricing-Analysis.git
4. *Any other comments?*
	- No

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is publicly available for download.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	-  It is distributed in CSV and SQLite formats. No DOI found.
3. *When will the dataset be distributed?*
	- The dataset was made available on February 28, 2024
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is provided under MIT, encouraging academic and legal use.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- There are no known restrictions imposed by third parties.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply.
7. *Any other comments?*
	- While efforts will be made to maintain the dataset, its long-term availability depends on continued project support and hosting arrangements
